### 2015-07-20 limitations.tex
various small tweaks

In future work we will investigate adding a SAT solver to Spack's
concretization process to present users with better options.  In our
experience, however, complex policy interactions like these are very
rare.

>>>>

Spack's current implementation has several limitations.
As mentioned in Section~\ref{sec:concretization}, we use a greedy 
concretization algorithm. For example, if package {\tt P} depends on 
both {\tt hwloc@1.9} and {\tt mpi}, and if the algorithm
chooses an MPI implementation for {\tt P} that depends strictly on
{\tt hwloc@1.8}, a conflict on {\tt hwloc} arises. In this case, Spack 
raises an error and the user must resolve the issue. Our implementation 
does not backtrack to find an MPI version that does not conflict. These 
cases have been rare so far. However, we plan to add better constraint
satisfaction solving to Spack in future work.

While Spack supports different architectures as part of the 
configuration space, we cannot currently factor common preferences (like 
{\tt configure} arguments and architecture-specific compiler flags) out of 
packages and into separate architecture descriptions, which leads to some 
clutter in the package files when too many per-platform conditions accumulate.
We are adding features that will further simplify Spack's build templates
for cross-platform installations.

Spack can require more disk space than a module-based system, as otherwise 
identical packages with different dependencies must be built separately. In 
our view, the significant reduction in complexity for the end user justifies 
this cost.

The use of Python has been a barrier for some users, and
a major attraction for others. For those who would otherwise create local
workarounds, Python's flexibility has allowed them to extend local
Spack packages to suit their needs. Such customizations frequently
guide our priorities for new core features. The
benefits of using a popular, rapidly emerging HPC language for our
embedded DSL outweigh any costs of the learning curve.

In the near term, we are actively working to grow a community around Spack 
and to build a larger base of contributors. On the technical side, we will
increase build robustness by deploying a continuous testing system
at LLNL.  Finally, to support the growing number of
HPC languages, runtimes, and programming models, we will add
capabilities to Spack that allow packages to depend on particular
compiler features.  More and more, our codes are beginning to rely
on advanced compiler capabilities, like {\tt C++11} language features,
OpenMP versions, and GPU compute capabilities. Ideally, Spack
will find suitable compilers and ensure ABI consistency when many
such features are in use.
